Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies

### 2021-06-24 main.tex
Lots of types fixed in main manuscript Removed the requirements of the system model - measurement vec/mat now have unknown dimension and have been written with 0...0 for the sections where this is the case - author's responses have been changed to reflect this Results sections updated to point out that the plotted track is only a sample track

Our contribution in this work presents a range-only localisation method meeting formal cryptographic requirements that ensure sensors keep their measurements and locations private while the navigator keeps its estimates private. We first define a novel notion for private linear combination aggregation, satisfying these cryptographic requirements, before using it to derive a filter based on the Extended Kalman Filter, with no hierarchical sensor layout assumptions. The linear combination aggregation scheme we put forward is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition capturing communication assumptions and leakages is given, crucial for cryptographic security. To the best of the authors' knowledge, no existing method for Bayesian state estimation using range-only sensors and meeting the desired privacy requirements exists.

@@

At every \textit{instance} $t$ (used to distinguish from an estimation \textit{timestep}), the navigator first broadcasts $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ to all sensors $1\leq i\leq n$, who individually compute linear combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ based on their measurement data $a_{j,i}$. Linear combinations are then sent back to the navigator, who computes their sum $\sum^n_{i=1}l^{(t)}_{i}$. This two-step linear combination aggregation protocol has been visually displayed in figure \ref{fig:agg_steps}.
\begin{figure}[htbp]
\centering
\begin{tikzpicture}[font=\footnotesize,scale=0.95]
    % Step 1
    \node at (3.25,5.5) {1. Broadcast and Combination Step};
    % Navigator
    \fill (3.25,4.75) [green!80!black!60] ellipse (0.4 and 0.4);
    \pic[xscale=0.22,yscale=0.3] at (3.25,4.9225) {plane};
    % Sensors
    \node at (1.5,1.375) {Sensor $1$};
    \fill [blue!80!black!40] (0.25,1.625) rectangle (2.875,2.625);
    \node at (1.625,2.125) {$\displaystyle l_1^{(t)} \!=\! \sum^m_{j=1}a_{1,j}^{(t)}\omega_j^{(t)}$};
    \node at (5,1.375) {Sensor $n$};
    \fill [blue!80!black!40] (3.625,1.625) rectangle (6.25,2.625);
    \node at (5,2.125) {$\displaystyle l_n^{(t)} \!=\! \sum^m_{j=1}a_{n,j}^{(t)}\omega_j^{(t)}$};
    \fill [black] (3.5,2.125) circle (0.05);
    \fill [black] (3,2.125) circle (0.05);
    \fill [black] (3.25,2.125) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,4.25) (5,2.875)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,4.25) (1.5,2.875)};
    \fill [lightgray] (2.125,3.875) rectangle (4.375,3.125);
    \node at (3.25,3.5) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};

@@

    % Bounding rectangles
    \draw [gray] (0,6) rectangle (6.5,1);
    \draw [gray] (0,0.75) rectangle (6.5,-4.25);
\end{tikzpicture}
\caption{Required linear combination aggregation steps at instance $t$.}
\label{fig:agg_steps}
\end{figure}
In addition, we note that an alternative approach to the two-step protocol is computing $\sum^{m}_{j=1}(\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)})$ at the navigator, requiring only values $a_{i,j}^{(t)}, 1 \leq j \leq m$ to be sent from each sensor $i$. We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in section \ref{sec:priv_localization}.

@@

We are now ready to define the type of encryption scheme we want for the specified communication protocol and the security guarantees it should provide. We let a linear combination aggregation scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$. These will be used by a trusted setup party, the navigator and sensors $i,\,1\leq i \leq n$. They are defined as follows.
\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the number of weights $m$, the navigator's public and private keys $pk_0$ and $sk_0$ and the sensor private keys $sk_i,\,1\leq i \leq n$.
    \item[$\mathsf{Enc}(pk_0, x)$] The navigator and sensors can encrypt any value $x$ with the navigator's public key $pk_0$ and obtain the encryption $\mathcal{E}_{pk_0}(x)$.
    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] At instance $t$, sensor $i$ computes and obtains the encrypted linear combination $l^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] At instance $t$, the navigator computes the aggregation of linear combinations $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
\end{LaTeXdescription}
The security notions we want the above algorithms to meet reflect the previously stated estimation privacy goals. The navigator should learn no information from individual sensors while sensors should learning no information from the navigator or any other sensors. In the context of the introduced communication protocol, this can be summarised as the following notions.
\begin{LaTeXdescription}
    \item[Indistinguishable Weights] No colluding subset of sensors gains any new knowledge about the navigator weights $\omega^{(t)}_j,\,1\leq j \leq m$ when receiving only their encryptions from the current and previous instances, and having the ability to encrypt plaintexts of their choice.
    \item[Linear Combination Aggregator Obliviousness] No colluding subset \textit{excluding} the navigator gains additional information about the remaining sensor values to be weighted, $a^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances. Any colluding subset \textit{including} the navigator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$.
\end{LaTeXdescription}
While indistinguishable weights can be achieved by encrypting weights with an encryption scheme meeting the notion of Indistinguishability under the Chosen Ciphertext Attack (IND-CPA) \cite{katzIntroductionModernCryptography2008}, the novel notion of Linear Combination Aggregator Obliviousness (LCAO) has been formalised as a typical cryptographic game between attacker and challenger in appendix \ref{app:lcao}. Lastly, we conclude the cryptographic problem definition with the following important remark.
\begin{remark}
    A leakage function including weights from the navigator requires extra care to be taken when giving its definition. If an attacker compromises the navigator, they have control over the weights, and therefore the leakage function. We note that in the leakage function above, $\sum^n_{i=1}\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by an attacker, \textit{e.g.}, $\sum^n_{i=1}a^{(t)}_{i,1}$ given weights $(1,0,\dots,0)$, but that individual sensor values $a^{(t)}_{i,j}$ remain private due to the assumption of a consistent broadcast.
\end{remark}

@@

\subsection{Estimation problem} \label{subsec:est_problem}
The estimation problem we consider, for which we will reduce communication to the protocol above, is localisation with range-only sensors. In this work, we will focus on the two-dimensional case for simplicity but will derive methods suitable for extension to a three-dimensional equivalent. The state that we wish to estimate captures the navigator position, and the change in position ($\Delta$), and is given by
\begin{equation}
    \vec{x} = 
    \begin{bmatrix}
        x & \Delta x & y & \Delta y
    \end{bmatrix}^\top\,. \label{eqn:state_definition}
\end{equation}
The state evolves following a known system model, which at timestep $k$ is given by
\begin{equation}
    \vec{x}_k = \vec{f}_k(\vec{x}_{k-1})+\vec{w}_k\,, \label{eqn:system_model}
\end{equation}
with system noise that is zero mean and has covariance $\mathsf{Cov}[\vec{w}_k]=\mat{Q}_k$. Measurements of the system follow a measurement model dependent on sensor $i$, $0\leq i \leq n$, given by 
\begin{equation}
    z_{k,i} = h_i(\vec{x}_k)+v_{k,i}\,, \label{eqn:measurement_model}
\end{equation}
with Gaussian measurement noises $v_{k,i} \sim \mathcal{N}(0,r_{k,i})$ and measurement function
\begin{equation}
    \begin{split}
        h_i(\vec{x}) &= \left\lVert
        \begin{bmatrix}
            x & y
        \end{bmatrix}^\top
        - \vec{s}_{i}\right\rVert \\
        &= \sqrt{(x-s_{x,i})^2 + (y-s_{y,i})^2}\,,
    \end{split}
\end{equation}
where
\begin{equation}
    \vec{s}_i = 
    \begin{bmatrix}
        s_{x,i} & s_{y,i}
    \end{bmatrix}^\top
\end{equation} 
is the location of sensor $i$.

@@

In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall a_1,a_2 \in \mathbb{Z}_N$,
\begin{align}
    \mathcal{D}(\mathcal{E}(a_1)\mathcal{E}(a_2) \hspace{-7pt} \pmod{N^2}) &= a_1+a_2 \hspace{-7pt} \pmod{N}\,, \\
    \mathcal{D}(\mathcal{E}(a_1)g^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1+a_2\hspace{-7pt}\pmod{N}\,, \label{eqn:paillier_hom_plain_add}\\
    \mathcal{D}(\mathcal{E}(a_1)^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1a_2 \hspace{-7pt} \pmod{N}\,. \label{eqn:paillier_hom_mult}
\end{align}

@@

Key generation is computed by first choosing two equal length and sufficiently large primes $p$ and $q$, and computing $N=pq$. A hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined and the public key is set to $(N, H)$. $n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to $n$ participants (whose values are to be aggregated), while the last key is set as
\begin{equation}
    sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}\,,
\end{equation}
and sent to the aggregator.

@@

When all encryptions $c^{(t)}_{i},\,1\leq i \leq n$ are sent to the aggregator, summation and decryption are computed by the functions
\begin{equation}
    c^{(t)} = H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2} \label{eqn:agg_summation}
\end{equation}
and
\begin{equation}
    \sum^{n}_{i=1}a^{(t)}_{i} = \frac{c^{(t)}-1}{N} \pmod{N}\,. \label{eqn:agg_decryption}
\end{equation}
Correctness follows from $\sum^{n}_{i=0}sk_i = 0$, and thus
\begin{equation*}
    \begin{split}
        &H(t)^{sk_0}\prod^{n}_{i=1}c_{i,t} \pmod{N^2} \\
        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{a_{i,t}} H(t)^{sk_i} \pmod{N^2} \\
        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}g^{a_{i,t}} \pmod{N^2} \\
        \equiv &(N+1)^{\sum^n_{i=1}a_{i,t}} \pmod{N^2}\,,
    \end{split}
\end{equation*}
removing all noise terms.

@@

The function for \textit{combined} quantization and encoding, $\mathsf{E}_{M,\phi,d}(a)$, of a given number $a \in \mathbb{R}$, for an integer range $\mathbb{Z}_M$, precision $\phi$ and scaling for $d$ prior encoded multiplications, is given by
\begin{equation}
    \mathsf{E}_{M,\phi,d}(a) = \left\lfloor \phi^{d+1} a \right\rceil \pmod{M}\,. \label{eqn:encode}
\end{equation}
Decoding of an integer $u \in \mathbb{Z}_M$, is given by
\begin{equation}
    \mathsf{E}^{-1}_{M,\phi,d}(u) \!=\! 
    \begin{dcases}
        \frac{u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &u\hspace{-8pt}\pmod{M} \leq \left\lfloor\frac{M}{2}\right\rfloor \\
        -\frac{M - u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &\text{otherwise} \\
    \end{dcases}.\label{eqn:decode}
\end{equation}

This encoding scheme provides the following homomorphic operations,
\begin{equation}
    \begin{split}
        \mathsf{E}_{M,\phi,d}(a_1) + \mathsf{E}_{M,\phi,d}(a_2)& \pmod{M} =\\
        &\mathsf{E}_{M,\phi,d}(a_1+a_2)
    \end{split}\label{eqn:encoding_homomorphic_add}
\end{equation}
and
\begin{equation}
    \begin{split}
        \mathsf{E}_{M,\phi,d}(a_1)\mathsf{E}_{M,\phi,d}(a_2)& \pmod{M} =\\
        &\mathsf{E}_{M,\phi,d+1}(a_1a_2)\,,
    \end{split}
\end{equation}
noting that when $M=N$, the modulus corresponds with those in the Paillier homomorphic operations \eqref{eqn:paillier_hom_plain_add}, \eqref{eqn:paillier_hom_mult} and the Joye-Libert sum \eqref{eqn:agg_decryption}.

@@

\section{Private Linear Combination Aggregation Scheme} \label{sec:lcao_scheme}
In this section, we introduce an encryption scheme meeting the desired security properties in section \ref{subsec:crypto_problem}. The scheme is a combination of the Paillier and Joye-Libert schemes and provides encrypted weights meeting IND-CPA and encrypted aggregation meeting LCAO. Similarly to its constituents, the scheme bases its security on the DCRA and, as with the Joye-Libert scheme, requires a trusted party for initial key generation and distribution. The four algorithms defining our scheme are given as follows.
\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$. Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose a the number of weights to combine, $m>1$, and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$. Sensor secret keys are generated by choosing $sk_i,\,1\leq i\leq n-1$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.

@@

    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] Encrypted linear combination at instance $t$ is computed as 
    \begin{equation}
        l^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{a^{(t)}_{i,j}} \pmod{N^2}\,,\label{eqn:our_scheme_lin_comb}
    \end{equation}
    and makes use of the homomorphic property \eqref{eqn:paillier_hom_mult}. Correctness follows from
    \begin{equation*}
        \begin{split}
             l^{(t)}_i &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{a^{(t)}_{i,j}} \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(a^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{a^{(t)}_{i,j}\omega^{(t)}_j} \rho^{N}_{j} \pmod{N^2} \\
            &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j} \rho_{i}^{N} \pmod{N^2}\,,
        \end{split}
    \end{equation*}
    for some values $\rho_i,\rho_j \in \mathbb{Z}_N\,,1\leq j \leq m$. Here, $\rho_i^N$ and $H(t)^{sk_i}$ can be considered the noise terms corresponding to the two levels of encryption from $pk_0$ and $sk_i$, respectively.

>>>>

Our contribution in this work presents a range-only localisation method meeting formal cryptographic requirements that ensure sensors keep their measurements and locations private while the navigator keeps its estimates private. We first define a novel notion for private linear combination aggregation, satisfying these cryptographic requirements, before using it to derive a filter based on the Extended Kalman Filter, with no hierarchical sensor layout assumptions. The linear combination aggregation scheme we put forward is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition capturing different communication assumptions and leakages is given, crucial for cryptographic security. To the best of the authors' knowledge, no existing method for Bayesian state estimation using range-only sensors and meeting the desired privacy requirements exists.

@@

At every \textit{instance} $t$ (used to distinguish from an estimation \textit{timestep}), the navigator first broadcasts $m$ weights $\omega_j^{(t)}, j\in\{1,\dots,m\}$ to all sensors $i\in\{1,\dots,n\}$, who individually compute linear combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ based on their measurement data $a_{j,i}$. Linear combinations are then sent back to the navigator, who computes their sum $\sum^n_{i=1}l^{(t)}_{i}$. This two-step linear combination aggregation protocol has been visually displayed in figure \ref{fig:agg_steps}.
\begin{figure}[htbp]
\centering
\begin{tikzpicture}[font=\footnotesize,scale=0.95]
    % Step 1
    \node at (3.25,5.5) {1. Broadcast and Combination Step};
    % Navigator
    \fill (3.25,4.75) [green!80!black!60] ellipse (0.4 and 0.4);
    \pic[xscale=0.22,yscale=0.3] at (3.25,4.9225) {plane};
    % Sensors
    \node at (1.5,1.375) {Sensor $1$};
    \fill [blue!80!black!40] (0.25,1.625) rectangle (2.875,2.625);
    \node at (1.625,2.125) {$\displaystyle l_1^{(t)} \!=\! \sum^m_{j=1}a_{1,j}^{(t)}\omega_j^{(t)}$};
    \node at (5,1.375) {Sensor $n$};
    \fill [blue!80!black!40] (3.625,1.625) rectangle (6.25,2.625);
    \node at (5,2.125) {$\displaystyle l_n^{(t)} \!=\! \sum^m_{j=1}a_{n,j}^{(t)}\omega_j^{(t)}$};
    \fill [black] (3.5,2.125) circle (0.05);
    \fill [black] (3,2.125) circle (0.05);
    \fill [black] (3.25,2.125) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,4.25) (5,2.875)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,4.25) (1.5,2.875)};
    \fill [lightgray] (2.125,3.875) rectangle (4.375,3.125);
    \node at (3.25,3.5) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};

@@

    % Bounding rectangles
    \draw [gray] (0,6) rectangle (6.5,1);
    \draw [gray] (0,0.75) rectangle (6.5,-4.25);
\end{tikzpicture}
\caption{Required linear combination aggregation steps at instance $t$.}
\label{fig:agg_steps}
\end{figure}
In addition, we note that an alternative approach to the two-step protocol is computing $\sum^{m}_{j=1}(\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)})$ at the navigator, requiring only values $a_{i,j}^{(t)}, j\in\{1,\dots,m\}$ to be sent from each sensor $i$. We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in section \ref{sec:priv_localization}.

@@

We are now ready to define the type of encryption scheme we want for the specified communication protocol and the security guarantees it should provide. We let a linear combination aggregation scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$. These will be used by a trusted setup party, the navigator and sensors $i\in\{1,\dots,n\}$. They are defined as follows.
\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input of security parameter $\kappa$, generate public parameters $\mathsf{pub}$, the number of weights $m$, the navigator's public and private keys $pk_0$ and $sk_0$ and the sensor private keys $sk_i,\,i\in\{1,\dots,n\}$.
    \item[$\mathsf{Enc}(pk_0, x)$] The navigator and sensors can encrypt any value $x$ with the navigator's public key $pk_0$ and obtain the encryption $\mathcal{E}_{pk_0}(x)$.
    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] At instance $t$, sensor $i$ computes and obtains the encrypted linear combination $l^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] At instance $t$, the navigator computes the aggregation of linear combinations $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
\end{LaTeXdescription}
The security notions we want the above algorithms to meet reflect the previously stated estimation privacy goals. The navigator should learn no information from individual sensors while sensors should learn no information from the navigator or any other sensors. In the context of the introduced communication protocol, this can be summarised as the following notions.
\begin{LaTeXdescription}
    \item[Indistinguishable Weights] No colluding subset of sensors gains any new knowledge about the navigator weights $\omega^{(t)}_j,\,j\in\{1,\dots,m\}$ when receiving only their encryptions from the current and previous instances, and having the ability to encrypt plaintexts of their choice.
    \item[Linear Combination Aggregator Obliviousness] No colluding subset \textit{excluding} the navigator gains additional information about the remaining sensor values to be weighted, $a^{(t)}_{i,j},\,j\in\{1,\dots,m\}$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances. Any colluding subset \textit{including} the navigator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$.
\end{LaTeXdescription}
While indistinguishable weights can be achieved by encrypting weights with an encryption scheme meeting the notion of Indistinguishability under the Chosen Ciphertext Attack (IND-CPA) \cite{katzIntroductionModernCryptography2008}, the novel notion of Linear Combination Aggregator Obliviousness (LCAO) has been formalised as a typical cryptographic game between attacker and challenger in appendix \ref{app:lcao}. Lastly, we conclude the cryptographic problem definition with the following important remark.
\begin{remark}
    A leakage function including weights from the navigator requires extra care to be taken when giving its definition. If an attacker compromises the navigator, they have control over the weights, and therefore the leakage function. We note that in the leakage function above, $\sum^n_{i=1}\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by an attacker, \textit{e.g.}, $\sum^n_{i=1}a^{(t)}_{i,1}$ given weights $(1,0,\dots,0)$, but that individual sensor values $a^{(t)}_{i,j}$ remain private due to the assumption of a consistent broadcast.
\end{remark}

@@

\subsection{Estimation problem} \label{subsec:est_problem}
The estimation problem we consider, for which we will reformulate communication to the protocol above, is localisation with range-only sensors. In this work, we will focus on the two-dimensional case for simplicity but will derive methods suitable for extension to a three-dimensional equivalent. The state that we wish to estimate must capture the navigator position, $x$ and $y$, and may contain any other components relevant to the system. It is of the form
\begin{equation}
    \vec{x} = 
    \begin{bmatrix}
        x & y & \cdots
    \end{bmatrix}^\top\,. \label{eqn:state_definition}
\end{equation}
This state evolves following some known system model, which at timestep $k$ can be written as
\begin{equation}
    \vec{x}_k = \vec{f}_k(\vec{x}_{k-1}, \vec{w}_k)\,, \label{eqn:system_model}
\end{equation}
with noise term $\vec{w}_k$. Measurements of the system follow a measurement model dependent on sensor $i\in\{1,\dots,n\}$, given by 
\begin{equation}
    z_{k,i} = h_i(\vec{x}_k)+v_{k,i}\,, \label{eqn:measurement_model}
\end{equation}
with Gaussian measurement noises $v_{k,i} \sim \mathcal{N}(0,r_{k,i})$ and measurement function
\begin{equation}
    \begin{split}
        h_i(\vec{x}) &= \left\lVert
        \begin{bmatrix}
            x & y
        \end{bmatrix}^\top
        - \vec{s}_{i}\right\rVert \\
        &= \sqrt{(x-s_{x,i})^2 + (y-s_{y,i})^2}\,,
    \end{split}
\end{equation}
where
\begin{equation}
    \vec{s}_i = 
    \begin{bmatrix}
        s_{x,i} & s_{y,i}
    \end{bmatrix}^\top
\end{equation} 
is the location of sensor $i$.

@@

In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall a_1,a_2 \in \mathbb{Z}_N$,
\begin{align}
    \mathcal{D}(\mathcal{E}(a_1)\mathcal{E}(a_2) \hspace{-7pt} \pmod{N^2}) &= a_1+a_2 \hspace{-7pt} \pmod{N}\,, \label{eqn:paillier_hom_add}\\
    \mathcal{D}(\mathcal{E}(a_1)g^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1+a_2\hspace{-7pt}\pmod{N}\,, \label{eqn:paillier_hom_plain_add}\\
    \mathcal{D}(\mathcal{E}(a_1)^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1a_2 \hspace{-7pt} \pmod{N}\,. \label{eqn:paillier_hom_mult}
\end{align}

@@

Key generation is computed by first choosing two equal length and sufficiently large primes $p$ and $q$, and computing $N=pq$. A hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined and the public key is set to $(N, H)$. $n$ private keys are generated by choosing $sk_i,\,i\in\{1,\dots,n\}$, uniformly from $\mathbb{Z}_{N^2}$ and distributing them to $n$ participants (whose values are to be aggregated), while the last key is set as
\begin{equation}
    sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}\,,
\end{equation}
and sent to the aggregator.

@@

When all encryptions $c^{(t)}_{i},\,i\in\{1,\dots,n\}$ are sent to the aggregator, summation and decryption of the aggregated sum are computed by the functions
\begin{equation}
    c^{(t)} = H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2} \label{eqn:agg_summation}
\end{equation}
and
\begin{equation}
    \sum^{n}_{i=1}a^{(t)}_{i} = \frac{c^{(t)}-1}{N} \pmod{N}\,. \label{eqn:agg_decryption}
\end{equation}
Correctness follows from $\sum^{n}_{i=0}sk_i = 0$, and thus
\begin{equation*}
    \begin{split}
        &H(t)^{sk_0}\prod^{n}_{i=1}c_{i,t} \pmod{N^2} \\
        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{a_{i,t}} H(t)^{sk_i} \pmod{N^2} \\
        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}(N+1)^{a_{i,t}} \pmod{N^2} \\
        \equiv &(N+1)^{\sum^n_{i=1}a_{i,t}} \pmod{N^2}\,,
    \end{split}
\end{equation*}
removing all noise terms.

@@

The function for \textit{combined} quantization and encoding, $\mathsf{E}_{M,\phi,d}(a)$, of a given number $a \in \mathbb{R}$ and with an integer range $\mathbb{Z}_M$, precision $\phi$ and scaling for $d$ prior encoded multiplications is given by
\begin{equation}
    \mathsf{E}_{M,\phi,d}(a) = \left\lfloor \phi^{d+1} a \right\rceil \pmod{M}\,. \label{eqn:encode}
\end{equation}
Decoding of an integer $u \in \mathbb{Z}_M$, is given by
\begin{equation}
    \mathsf{E}^{-1}_{M,\phi,d}(u) \!=\! 
    \begin{dcases}
        \frac{u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &u\hspace{-8pt}\pmod{M} \leq \left\lfloor\frac{M}{2}\right\rfloor \\
        -\frac{M - u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &\text{otherwise} \\
    \end{dcases}.\label{eqn:decode}
\end{equation}

This encoding scheme provides the following homomorphic operations,
\begin{equation}
    \begin{split}
        \mathsf{E}_{M,\phi,d}(a_1) + \mathsf{E}_{M,\phi,d}(a_2)& \pmod{M} =\\
        &\mathsf{E}_{M,\phi,d}(a_1+a_2)
    \end{split}\label{eqn:encoding_homomorphic_add}
\end{equation}
and
\begin{equation}
    \begin{split}
        \mathsf{E}_{M,\phi,d}(a_1)\mathsf{E}_{M,\phi,d}(a_2)& \pmod{M} =\\
        &\mathsf{E}_{M,\phi,d+1}(a_1a_2)\,,
    \end{split}
\end{equation}
noting that when $M=N$, the operations and modulus correspond with those in the Paillier homomorphic operations \eqref{eqn:paillier_hom_add}, \eqref{eqn:paillier_hom_plain_add} and \eqref{eqn:paillier_hom_mult}, and the Joye-Libert sum \eqref{eqn:agg_decryption}.

@@

\section{Private Linear Combination Aggregation Scheme} \label{sec:lcao_scheme}
In this section, we introduce an encryption scheme meeting the desired security properties in section \ref{subsec:crypto_problem}. The scheme is a combination of the Paillier and Joye-Libert schemes and provides encrypted weights meeting IND-CPA and encrypted aggregation meeting the notion of LCAO defined in section \ref{subsec:crypto_problem}. Similarly to its constituents, the scheme bases its security on the DCRA and, as with the Joye-Libert scheme, requires a trusted party for initial key generation and distribution. The four algorithms defining our scheme are given as follows.
\begin{LaTeXdescription}
    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$. Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose a the number of weights to combine, $m>1$, and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$. Sensor secret keys are generated by choosing $sk_i,\,i\in\{1,\dots,n-1\}$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.

@@

    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] Encrypted linear combination at instance $t$ is computed as 
    \begin{equation}
        l^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{a^{(t)}_{i,j}} \pmod{N^2}\,,\label{eqn:our_scheme_lin_comb}
    \end{equation}
    and makes use of the homomorphic property \eqref{eqn:paillier_hom_mult}. Correctness follows from
    \begin{equation*}
        \begin{split}
             l^{(t)}_i &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{a^{(t)}_{i,j}} \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(a^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{a^{(t)}_{i,j}\omega^{(t)}_j} \rho^{N}_{j} \pmod{N^2} \\
            &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j} \rho_{i}^{N} \pmod{N^2}\,,
        \end{split}
    \end{equation*}
    for some values $\rho_i,\rho_j \in \mathbb{Z}_N,\,j\in\{1,\dots,m\}$. Here, $\rho_i^N$ and $H(t)^{sk_i}$ can be considered the noise terms corresponding to the two levels of encryption from $pk_0$ and $sk_i$, respectively.
